### 2013-10-21 Rcode/ash.test.rmd
modified mix.R to remove require(truncnorm); amended README to note need for truncnorm

system.time((beta.ash.vb.null = ash(ss$betahat, ss$betasd, VB=TRUE, prior=NULL)))
system.time((beta.ash.vb.null2 = ash(ss$betahat, ss$betasd, VB=TRUE, prior=NULL)))
expect_that(beta.ash.vb.null$PosteriorMean, equals(beta.ash.vb.null2$PosteriorMean))
expect_that(beta.ash.vb.null$qvalue, equals(beta.ash.vb.null2$qvalue))
expect_that(beta.ash.vb.null$PositiveProb, equals(beta.ash.vb.null2$PositiveProb))

>>>>

system.time((beta.ash.vb.null = ash(ss$betahat, ss$betasd, VB=TRUE, prior="nullbiased")))
system.time((beta.ash.vb.null2 = ash(ss$betahat, ss$betasd, VB=TRUE, prior="nullbiased")))
expect_that(beta.ash.vb.null$PosteriorMean, equals(beta.ash.vb.null2$PosteriorMean))
expect_that(beta.ash.vb.null$qvalue, equals(beta.ash.vb.null2$qvalue))
expect_that(beta.ash.vb.null$PositiveProb, equals(beta.ash.vb.null2$PositiveProb))
